\section*{Abstract}

Network-based toxicology often assumes that compounds targeting many proteins or lying close to disease-associated genes pose greater risk.
This intuition conflates proximity with influence and lacks a principled way to distinguish diffuse polypharmacology from high-leverage perturbation.
Here, we evaluate this assumption using two major \textit{Hypericum perforatum} constituents, Hyperforin and Quercetin, as a controlled case study in hepatotoxicity (DILI) risk.

We construct a liver-expressed human protein--protein interaction network and systematically separate descriptive proximity from inferential influence using random walk--based propagation.
Although Quercetin targets more proteins and exhibits closer shortest-path proximity to DILI-associated genes at the primary threshold ($\geq$900), it exerts weaker network influence than Hyperforin.
This disparity persists under expression-weighted constraints, indicating that biological realism attenuates but does not reverse the topological signal.

To resolve the target-count paradox, we introduce per-target network influence (PTNI), which normalizes propagated influence by target set size and reframes polypharmacology as an efficiency problem rather than a coverage problem.
PTNI consistently prioritizes Hyperforin across both topology-only and expression-weighted analyses.
Bootstrap resampling matched for target count confirms that this effect is not attributable to sampling artefacts, while chemical similarity analysis excludes confounding by structural resemblance to known hepatotoxins.

Together, these results demonstrate that network proximity is threshold-dependent and insufficient for toxicological prioritization, whereas influence rankings are robust and provide a more reliable criterion for identifying high-risk compounds.
This framework generalizes beyond \textit{H.\ perforatum} and offers a principled basis for integrating network topology, biological constraint, and robustness in computational safety assessment.

\vspace{0.5em}
\noindent\textbf{Keywords:} network pharmacology, hepatotoxicity, \textit{Hypericum perforatum}, Hyperforin, per-target network influence, drug-induced liver injury
