\section{Introduction}

Network-based toxicology is increasingly used to prioritize compounds for safety risk by mapping their molecular targets onto biological interaction networks \citep{Hopkins2008, Barabasi2011}.
A common heuristic underlying these approaches is that compounds interacting with many proteins, or lying in close network proximity to disease-associated genes, are more likely to pose adverse risk.
Though intuitive, this assumption conflates topological proximity with functional influence and provides no principled way to distinguish diffuse polypharmacology from high-leverage perturbation.
Whether proximity and target count meaningfully predict toxicological risk remains an open and testable question.

\textit{Hypericum perforatum} (St.\ John's Wort) provides a controlled system in which to examine this assumption.
The extract contains multiple bioactive constituents with contrasting pharmacological profiles \citep{Nahrstedt1997}, most notably the phloroglucinol Hyperforin and the flavonoid Quercetin.
Hyperforin interacts with a small number of targets and is a potent activator of the pregnane X receptor (PXR) \citep{Moore2000}, whereas Quercetin exhibits broad, distributed polypharmacology across dozens of proteins \citep{Boots2008}.
Both compounds exhibit hepatic activity, yet the constituent responsible for hepatotoxicity risk remains unresolved, with regulatory assessments and clinical reports offering incomplete or conflicting attribution \citep{Hammerness2003, Bauer2004, EMA2018}.

Existing network studies would predict greater risk for Quercetin based on its larger target set and closer proximity to liver injury--associated genes.
However, such predictions implicitly assume that all targets contribute equally and that network distance is a sufficient surrogate for downstream perturbation.
These assumptions ignore the topology of signal propagation within biological networks, where influence depends not only on distance, but also on how signals traverse highly connected and regulatory nodes.

Here, we explicitly separate descriptive proximity from inferential influence using random walk--based network propagation on a liver-expressed human protein--protein interaction network \citep{Kohler2008, Guney2016}.
Random walk with restart (RWR) captures the extent to which perturbations originating at compound targets diffuse through the network to a defined disease module, providing an influence-based metric that is not reducible to shortest-path distance alone.
To incorporate biological realism, we further constrain propagation by liver-specific gene expression.

To resolve the target-count paradox---where compounds with more targets may exert weaker functional effects---we introduce per-target network influence (PTNI), a normalization that quantifies influence efficiency rather than raw coverage.
PTNI reframes polypharmacology as an efficiency problem, distinguishing compounds that weakly perturb many nodes from those that exert strong leverage through a limited set of targets.

We apply this framework to compare Hyperforin (10 targets) and Quercetin (62 targets) across multiple analytical tiers, including proximity, influence, expression-weighted influence, PTNI, bootstrap sensitivity analysis, and chemical similarity controls.
This design allows us to test whether target count and proximity are sufficient predictors of hepatotoxic risk, or whether influence efficiency provides a more robust criterion for toxicological prioritization.
